Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed plot of outcomes measured

knitr::kable(outcomes_count)

#Plot the result
outcome_count_plot <- ggplot(data = outcomes_count) + 
  geom_point(aes(x = reorder(outcome_measured, 
                             num_of_studies), 
               y = num_of_studies
               ), 
           stat = 'identity',
           color = 'darkslategray4'
           ) +
  coord_flip() +
  theme_minimal()

plot(outcome_count_plot)
```

>>>>

knitr::kable(outcomes_count,
             caption = "Count of outcomes measured")
```
